---
title: "Two Parameters"
author: "Annika"
format: html
execute:
  echo: false
---

```{r}
#| message: FALSE

library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
nhanes |>
filter(sex == "Male", age >= 18) |>
select(height) |>
drop_na() |>
ggplot(aes(x = height)) +
geom_histogram(bins = 50) + 
labs(
title = "Male Adult Height in the US in 2010",
x = "Height (cm)",
y = "Count",
caption = "Source: National Health and Nutrition Examination Survey"
)
```

Using data from the National Health and Nutrition Examination Survey conducted from 2009 to 2011, we seek to create a model of height for adult men. In particular, what is the average height of an adult male in America in 2024? Since participation in the survey is voluntary, it could mean that, for example, taller men are more likely to answer this question. We modeled height using an intercept-only regression.

```{r}
#| cache: TRUE

fit_male_height <- brm(formula = height ~ 1, data = nhanes, family = gaussian(), silent = 2, refresh = 0, seed = 12)


```

```{r}
tbl_regression(fit_male_height, intercept = TRUE)

```


```{r}
#| label: plot

ndata <- tibble(.rows = 1)

fit_male_height |>
add_predicted_draws(newdata = ndata) |>
ggplot(aes(x = .prediction)) + 
geom_histogram(aes(y = after_stat(count / sum(count))), bins = 100) + 
labs(
title = "Posterior for Max Height Difference Among Four Men",
subtitle = "The expected value for this difference would be much more narrow",
x = "Height difference in centimeters",
y = "Probability",
caption = "Data source: NHANES"
) + 
scale_x_continuous(labels = scales::number_format()) + 
scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```

```{r}
fit_male_height |>
add_predicted_draws(newdata = ndata) |>
mutate(tall = if_else(.prediction > 180, TRUE, FALSE)) |>
summarize(odds = mean(tall))
```

